---
title: "Cooper Gant"
output: html_document
date: "2025-05-01"
---

A demo notebook for Dow Jones News Fund data interns

During the week’s training, you will work on a project called Investigate Your Community to produce detailed story pitches relevant to their summer internship positions. The goal is to have the students research a topic relevant to your newsroom so they can get to work immediately at the internship. 

Here are some examples from last year’s DJNF data journalism training:

Hannah Rosenberger, at ASI Media/Counselor magazine, produced this analysis on name, image and likeness trends: https://hrosenberger.github.io/ASI-NIL-Project/

Shifra Dayak, an intern at the Connecticut Mirror, produced this analysis of environment spill data: https://shifradayak.github.io/DJNF_Merrill/ct_env_spills.html.

Michael Zhang, an intern at the Houston Landing, explored local election data: https://michaelzhangreporter.github.io/Houston_Campaign_Finance/


Here's what your newsroom suggested for a project

Here are a couple stories Cooper could pursue for us during his internship.
Two things are possible data-driven news stories, one involves Buc-ee's.

Thing one: Broadband service 
I'd like to see us produce a story that evaluates the status of broadband data service in Arkansas.
All we've really reported is that there are rural areas [and some decent size cities] that remain years behind because of expense and challenging terrain.
Broadband service providers face the same challenges that slowed the creation of roads, electric service and phone service in Arkansas.
But we could go deeper than that, and try to explain why data speeds for many homes seem to be painfully slow, and not really broadband.

There's a state Broadband Office: broadband.arkansas.gov
It has a nifty map display: register.broadband.arkansas.gov/register/bead/map

Thing two: Electric vehicles
It would be interesting to compare the registration numbers for electric and electric hybrid vehicles in Arkansas.
Is Arkansas keeping up with the smaller comparable states, neighboring states, national average?
Same could be asked about creation of charging stations.

The Arkansas Department of Finance and Administration has all the data. We'd have to ask them for it.
The state charges a $200 a year fee for each electric vehicle, to make up for "lost" gas tax revenue, so there's probably data for the past few years to examine.

Thing three: Buc-ee's mania
Arkansas' first Buc-ee's is set to open later this year in relatively urban Benton, a suburb city of Little Rock.
Seems like many of the outsized Buc-ee's stores are built rural areas and those governments probably see measurable tax revenue boosts when they open.
Not sure where to go in the Buc-ee's infested states to find data to measure this Buc-ee's bump.
It may be too difficult to ascertain. 
Based on our metrics, any story with the word Buc-ee's in it will be extremely popular.



This notebook helps you get started on the electic vehicles

# Load software libraries
```{r}
#install.packages("tidyverse")
#install.packages("janitor")
#install.packages("readxl")
#install.packages("rvest")
library(tidyverse)
library(janitor)
library(readxl)
library(rvest)

```


# Load your data

2024

```{r}

# 
# YOUR_DATA <- read.csv("../data/XXXXX.csv") |> 
#     clean_names()

# data <- read_excel("../data/2024-12-Revenue.xlsx", skip=2) |> 
#     clean_names()

data <- read.csv("../data/ark_electric_hybrid.csv") |> 
    clean_names()


```

Data details:


# Explore the data types
```{r}

#glimpse(YOUR_DATA)

glimpse(data)

```
# pct of whole
```{r}
data <- data |> 
  mutate(pct = fully_electric/(hybrid+fully_electric))
```


# National context: All vehicle registrations
https://afdc.energy.gov/vehicle-registration

Scraper:

```{r}
#this pulls in data from that table

url2 <- "https://afdc.energy.gov/vehicle-registration"
test  <- url2 %>%
  read_html() %>%
  html_table() 

car_registrations <- test[[1]] %>%
  clean_names() 

```


#Clean headings
```{r}
new_headers <- as.character(car_registrations[1, ])
car_registrations_clean <- car_registrations[-(1), ] # Remove the first two rows
colnames(car_registrations_clean) <- new_headers

# Clear the row names
rownames(car_registrations_clean) <- NULL

car_registrations <- car_registrations_clean |> 
  clean_names()


```


# Part 2: Buc-ee's

Jim had a great idea about Buc-ee's. Make some calls to the county / city economic development officials to see what you can find about economic impact, tax revenue from opening a Buc-ee's store. Locations: https://buc-ees.com/locations/

It would be great to nail down the dollar impact in some of these communities.

https://communityplaymaker.com/discoveries/the-buc-ees-effect/#:~:text=When%20a%20community%20leader%20sees,million%20in%20indirect%20sales%20tax.



# Questions 

Write down questions you want answered:



# Data Details


