---
title: "Cooper Gant"
output: html_document
date: "2025-05-01"
editor_options: 
  markdown: 
    wrap: 72
---

Cooper Gant, June 2, 2025

**RSW comment: Hi Cooper, I will need to chat with you to focus the
question and the scope of this project. I don't follow what is going on
here. Thanks, Rob**

My story covers the difference between Arkansas’ increase in electric
vehicles [as a percentage point against the entirety of the
nation.]{.underline}rsw comment: I dont understand this "as a percentage
point"

The Natural State is lagging **##rsw comment: still not following what
this is about \##** at about half the year-to-year increase
percentage-wise in comparison to the national average on light-duty
electric vehicles – only being better than Mississippi in a border-state
comparison.

This story is timely due to the cuts of federal programs supporting
charging station development, [Elon Musk’s return to Tesla following a
shaky Q1 earnings call**,**]{.underline} **##rsw comment - rephrase or
cut. tesla's issues are of a different kind \##** and the national
rescinding of climate-conservation standards.

My target audience for this story includes environmental
conservationists, automotive industry enthusiasts, and electric vehicle
enthusiasts.

There is a wide assortment of sources that can comment on this story.
Scott Hardin of the Arkansas DFA**##rsw comment - spell out DFA and all
obscure acronyms \##**, small-town business owners that manage charging
stations, any of the environmental dynamics program staff at the
University of Arkansas at Fayetteville, current ARDOT **##rsw comment -
spell out DFA and all obscure acronyms \##**director Jared Wiley, and
former ARDOT director Lorie Tudor (she oversaw the organization during
the time of the collected data pool from 2019-2023).

The impact of this story not being reported is that we, as **#rsw
comment: Arkansas taxpayers or all taxpayers? \##** taxpayers, have paid
into the building of electric vehicle charges but do not have the same
driver infrastructure ratio as our neighboring states (excluding
Mississippi). However, the drivers pay a \$200, \$100, or \$50 “lost
gas” tax that goes back into road infrastructure and other similar
programs – so we can ask ARDOT if the lack thereof usage of the road
solely hurts non-EV drivers. Once I hear back from Scott Hardin, I will
know what percentage of the total revenue it makes up. However, it still
leaves many questions regarding how “worth it” it was for the state to
fund the amount of charging stations.

Additionally, for environmental conservationists, there are an
assortment of problems with other rural states, such as Alabama and
Tennessee, staying ahead of us in the EV percentage increase. Northwest
Arkansas has continued to grow as a technological **hub** ~~point~~ in
the South but lacks this specific statistic. Why is it that Alabama is
better than us? Are they putting even MORE charging stations or just
having better locations?

The visuals for this story will include an assortment of EVs charging
across the state. Showing a charger in Jonesboro, Texarkana, and
Fayetteville will emphasize how much was invested in the charging
programs. Also, a graphic showing the percentage climb of the nation,
Arkansas, and similar states will provide better context for readers.

There are a lot more steps to include in this. Including the
year-to-year gas revenue totals will be essential to telling the story
of how much money the state makes from EV owners to fund our state’s
road infrastructure. Another unique element is comparing the national
amount of electric vehicle charging stations per person in comparison to
how much the state is driving.

Also, I want to pull more statistics of Arkansas’ totals for different
hybrid types.

If I am unable to get the extra data mentioned, a realistic date for
this is within a week and a half. The interviews will be scheduled over
Zoom for the next week.

MY DATA/MATH Percentage of total vehicles that are EV (EV, hybrid and
plug-in hybrid)

**#RSW comment: let's make a graphic from this**

ARKANSAS Percentage of total vehicles that are EV (EV, hybrid and
plug-in hybrid) 2019 0.89%

2020 0.94%

2021 1.13%

2022 1.42%

2023 1.75%

NATION 2019 2.11%

2020 2.31%

2021 2.75%

2022 3.44%

2023 4.27%

------------------------------------------------------------------------

delete the template material

~~A demo notebook for Dow Jones News Fund data interns~~

~~During the week’s training, you will work on a project called
Investigate Your Community to produce detailed story pitches relevant to
their summer internship positions. The goal is to have the students
research a topic relevant to your newsroom so they can get to work
immediately at the internship.~~

~~Here are some examples from last year’s DJNF data journalism
training:~~

~~Hannah Rosenberger, at ASI Media/Counselor magazine, produced this
analysis on name, image and likeness trends:
<https://hrosenberger.github.io/ASI-NIL-Project/>~~

~~Shifra Dayak, an intern at the Connecticut Mirror, produced this
analysis of environment spill data:
<https://shifradayak.github.io/DJNF_Merrill/ct_env_spills.html>.~~

~~Michael Zhang, an intern at the Houston Landing, explored local
election data:
<https://michaelzhangreporter.github.io/Houston_Campaign_Finance/>~~

~~Here's what your newsroom suggested for a project~~

~~Here are a couple stories Cooper could pursue for us during his
internship. Two things are possible data-driven news stories, one
involves Buc-ee's.~~

~~Thing one: Broadband service I'd like to see us produce a story that
evaluates the status of broadband data service in Arkansas. All we've
really reported is that there are rural areas [and some decent size
cities] that remain years behind because of expense and challenging
terrain. Broadband service providers face the same challenges that
slowed the creation of roads, electric service and phone service in
Arkansas. But we could go deeper than that, and try to explain why data
speeds for many homes seem to be painfully slow, and not really
broadband.~~

~~There's a state Broadband Office: broadband.arkansas.gov It has a
nifty map display: register.broadband.arkansas.gov/register/bead/map~~

~~Thing two: Electric vehicles It would be interesting to compare the
registration numbers for electric and electric hybrid vehicles in
Arkansas. Is Arkansas keeping up with the smaller comparable states,
neighboring states, national average? Same could be asked about creation
of charging stations.~~

~~The Arkansas Department of Finance and Administration has all the
data. We'd have to ask them for it. The state charges a \$200 a year fee
for each electric vehicle, to make up for "lost" gas tax revenue, so
there's probably data for the past few years to examine.~~

~~Thing three: Buc-ee's mania Arkansas' first Buc-ee's is set to open
later this year in relatively urban Benton, a suburb city of Little
Rock. Seems like many of the outsized Buc-ee's stores are built rural
areas and those governments probably see measurable tax revenue boosts
when they open. Not sure where to go in the Buc-ee's infested states to
find data to measure this Buc-ee's bump. It may be too difficult to
ascertain. Based on our metrics, any story with the word Buc-ee's in it
will be extremely popular.~~

~~This notebook helps you get started on the electic vehicles~~

# Load software libraries

```{r}
#install.packages("tidyverse")
#install.packages("janitor")
#install.packages("readxl")
#install.packages("rvest")
library(tidyverse)
library(janitor)
library(readxl)
library(rvest)

```

# Load your data

2024

```{r}

# 
# YOUR_DATA <- read.csv("../data/XXXXX.csv") |> 
#     clean_names()

# data <- read_excel("../data/2024-12-Revenue.xlsx", skip=2) |> 
#     clean_names()

data <- read.csv("../data/ark_electric_hybrid.csv") |> 
    clean_names()


```

Data details:

# Explore the data types

```{r}

#glimpse(YOUR_DATA)

glimpse(data)

```

# pct of whole

```{r}
data <- data |> 
  mutate(pct = fully_electric/(hybrid+fully_electric))
```

# National context: All vehicle registrations

<https://afdc.energy.gov/vehicle-registration>

Scraper:

```{r}
#this pulls in data from that table

url2 <- "https://afdc.energy.gov/vehicle-registration"
test  <- url2 %>%
  read_html() %>%
  html_table() 

car_registrations <- test[[1]] %>%
  clean_names() 

```

#Clean headings

```{r}
new_headers <- as.character(car_registrations[1, ])
car_registrations_clean <- car_registrations[-(1), ] # Remove the first two rows
colnames(car_registrations_clean) <- new_headers

# Clear the row names
rownames(car_registrations_clean) <- NULL

car_registrations <- car_registrations_clean |> 
  clean_names()


```

# Part 2: Buc-ee's

Jim had a great idea about Buc-ee's. Make some calls to the county /
city economic development officials to see what you can find about
economic impact, tax revenue from opening a Buc-ee's store. Locations:
<https://buc-ees.com/locations/>

It would be great to nail down the dollar impact in some of these
communities.

<https://communityplaymaker.com/discoveries/the-buc-ees-effect/#>:\~:text=When%20a%20community%20leader%20sees,million%20in%20indirect%20sales%20tax.

# Questions

Write down questions you want answered:

# Data Details
